%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional Resume
% LaTeX Template
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.7in,right=0.5in,bottom=0.3in]{geometry} % Document margins
\usepackage{gensymb}
\usepackage{needspace}
\name{Anderson Garron} % Your name
\address{5507 Gallatin St, Hyattsville, MD 20781} % Your address
\address{856~-~369~-~6850 \\ anderson.garron@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Maryland, College Park} \hfill {\em May 2014, expected} \\ 
M.S. in Computer Science.\\
Overall GPA: 3.30/4.00

{\bf Ursinus College} \hfill {\em May 2012} \\ 
B.S. with Distinguished Honors in Computer Science. Major GPA: 3.83/4.00\\
B.S. in Mathematics. Major GPA: 3.44/4.00\\
Overall GPA: 3.46/4.00
\end{rSection}

\begin{rSection}{Skills}
\textbf{Languages:} C, C++, Python, Java, JavaScript, R, SQL\\
\textbf{Tools:} Eclipse, Git/GitHub/GitLab, SVN, LaTeX\\
\textbf{Operating Systems:} Ubuntu, Unix, Windows XP, Windows 7
\end{rSection}


%-----------------------------------------------------------
% RESEARCH EXPERIENCE SECTION
%-----------------------------------------------------------
\begin{rSection}{Projects}

\begin{rSubsection}{University of Maryland Research}{August 2012 - Present}{Graduate Research Assistant}{College Park, MD}
\item
\begin{rWorkProject}{Natural Language Processing for the Mental Health Domain (under Prof. Philip Resnik)}
\item Integrated language models and state-of-the-art topic modeling techniques in Python and Java to improve automatic diagnostic screening for depression in college students.
\item Demonstrated an 11\% improvement in neuroticism prediction (F-measure) over lexical-categorical approach (LIWC) (Resnik, Garron, and Resnik, 2013).
\item Worked with large scale data (over 25 million Facebook statuses) as part of a team in the University's CLIP lab, building and providing research software on a shared Unix filesystem.
\end{rWorkProject}
\item
\begin{rWorkProject}{Mobile Audio/Video Streaming for the Service Sector (under Prof. Ashok Agrawala)}
\item Designing a store-and-forward architecture that uses WebRTC to integrate audio/video feeds into emergency calls.
\item Implementing mobile client to place calls and web-based client to handle incoming calls and forward to field officers.
\item Working as part of a team using industry version control standards on a Unix development machine.
\end{rWorkProject}
\end{rSubsection}

\begin{rSubsection}{ReactLabs}{May 2013 - September 2013}{Software Contractor}{College Park, MD}
\item
\begin{rWorkProject}{Web-Based Charting Client for Live Polling Data}
\item Implemented web client for live charting of event-related polls, as acquired by ReactLabs mobile polling application. Made use of specialized JavaScript libraries for streaming and charting data.
\item Worked on front-end in tandem with collaborators at Palomino Labs building the data-providing back-end.
\end{rWorkProject}
\end{rSubsection}

%\newpage

\begin{rSubsection}{Ursinus College Research}{May 2009 - May 2012}{Undergraduate Research Assistant}{Collegeville, PA}
\item
\begin{rWorkProject}{Applying Machine Learning in the Legal Domain}
\item Awarded competitive funded summer fellowship to research the information retrieval (IR) technique Latent Semantic Indexing (LSI) in conjunction with machine learning techniques with a focus on the international IR Text REtrieval Conference (TREC). (Garron and Kontostathis, 2011 and 2012.)
\end{rWorkProject}
\item
\begin{rWorkProject}{Automatic Detection of Cyberbullying}
\item Worked as part of a team in improving and modifying a family of systems to accurately detect cyberbullies and sexual predators in online communications systems. This research focused on techniques in IR and
machine learning. (Kontostathis et al., 2012.)
\end{rWorkProject}
\end{rSubsection}
\end{rSection}


%-----------------------------------------
% WORK EXPERIENCE
%-----------------------------------------
\begin{rSection}{Work Experience}
\begin{rSubsection}{University of Maryland Computer Science Department}{August 2012 - Present}{Graduate Teaching Assistant}{College Park, MD}
\item
\begin{rWorkProject}{Graduate Course TA}
\item Supervised teams of graduate students in Machine Learning competitions with a focus on detecting mentally unhealthy Facebook users using status updates.
\item CMSC723 - Computational Linguistics I (Fall 2013)
\item CMSC773 - Computational Lingusitics II (Spring 2014)
\end{rWorkProject}
\item
\begin{rWorkProject}{Undergraduate Course TA}
\item TA for various undergraduate CS courses; responsibilities included giving twice-weekly lectures and grading projects.
\item CMSC216 - Introduction to Computer Systems (Fall 2012, Summer 2013)
\item CMSC250 - Discrete Structures (Spring 2013)
\end{rWorkProject}
\end{rSubsection}

\begin{rSubsection}{Ursinus College Information Technology}{August 2009-May 2012}{IT Help Desk Worker}{Collegeville, PA}
\item Worked directly with students and faculty in solving hardware and software problems on laptops and mobile devices. 
\end{rSubsection}
\end{rSection}


%----------------------------------------------------------------------------------------
%	SELECTED PUBLICATIONS
%----------------------------------------------------------------------------------------

% AMA Style
\begin{rSection}{Publications}
\textbf{Resnik, Garron, and Resnik.} Using Topic Modeling to Improve Prediction of Neuroticism and Depression in College Students. \textit{Poster, EMNLP 2013. Seattle, WA. October 2013.}
\item \textbf{Kontostathis, West, Garron, Reynolds, and Edwards.} Identifying Predators Using ChatCoder 2.0. \textit{Proceedings of CLEF 2012. Rome, Italy. September 2012.}
\item \textbf{Garron and Kontostathis.} Latent Semantic Indexing with Selective Query Expansion. \textit{Proceedings of the Text Mining Workshop 2012. Anaheim, CA. April 2012.}
\item \textbf{Garron and Kontostathis.} Applying Latent Semantic Indexing on the TREC 2011 Legal Dataset. \textit{Proceedings of the Twentienth Text Retrieval Conference. Bethesda, MD. November 2011.}
\end{rSection}

\begin{rSection}{Service \& Awards}
\textbf{Dean's Fellowship.} University of Maryland, College Park. 2012.
\item \textbf{Faculty Prize for Excellence in Computer Science.} Ursinus College CS Department, 2012.
\item \textbf{Executive Board, Phi Kappa Sigma International Fraternity.} Ursinus College, 2011-2012.
\item \textbf{President, Upsilon Pi Epsilon International Honor Society for the Computing and Information Disciplines.} Ursinus College, 2011-2012.
\end{rSection}
\end{document}
